---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mapindiatools

<!-- badges: start -->

[![R-CMD-check](https://github.com/shubhamdutta26/mapindiatools/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/shubhamdutta26/mapindiatools/actions/workflows/R-CMD-check.yaml)
[![Codecov test
coverage](https://codecov.io/gh/shubhamdutta26/mapindiatools/graph/badge.svg)](https://app.codecov.io/gh/shubhamdutta26/mapindiatools)

<!-- badges: end -->

The goal of `mapindiatools` is to serve as a container package for the
maps data used in `mapindia` package. This data has been separated to
keep the size of the `mapindia` package manageable and facilitate easier
maintenance, while enabling more frequent updates to the Indian map data
frame without relying on `mapindia` package updates.

## Map data

The geojson files are stored in the . The data was read using the `sf`
package, appropriately modified using the `build_mapping_data()`
function, and saved as .gpkg files in
[mapindiatoolsdata](https://github.com/shubhamdutta26/mapindiatoolsdata)
repository. The centroids were also calculated using the
`compute_centroids()` function. These files were then stored as internal
data in R/ folder.

**Note:** The 3-digit code11 codes for districts were merged with the
2-digit state codes to create a 5-digit code for the districts.

## Installation

To install mapindiatools from CRAN:

```{r}
#| label: cran
#| eval: false
install.packages("mapindiatools")
```

You can install the development version of mapindiatools from
[GitHub](https://github.com/) with:

```{r}
#| label: github
#| eval: false
# install.packages("pak")
pak::pak("shubhamdutta26/mapindiatools")
```

## Usage

To begin using `mapindiatools`, import the package using the `library`
command:

```{r}
#| label: usage
#| eval: false
library(mapindiatools)
```

## Acknowledgments

I would like to thank [pdil](https://github.com/pdil) since I have used
his `usmap` package to write most of the functions in this package. I
would also like to thank [datta07](https://github.com/datta07) for the
geojson files of the Indian subcontinent.
